%%
%% $Id: article.tex,v 1.1 2008/09/20 10:19:28 natalie Exp $
%% $Source: /Users/natalie/cvs/tex/templates/article.tex,v $
%% $Date: 2008/09/20 10:19:28 $
%% $Revision: 1.1 $
%%

%\documentclass[a4paper,11pt,BCOR1cm,DIV11,headinclude]{scrbook}
% bei 12pt ist DIV 12 default, bei 11pt ist es DIV 10
% Textbereiche 
% DIV 10: 147*207.9mm, DIV 11: 152.73*216mm, DIV 12:157.50*222.75
% DIV 13: 161.54*228.46mm, DIV 14: 165*233.36mm

\def\deftitle{Notes on hedging cryptos with spectral risk measures}
% \def\defauthor{N.\ Packham}
% \def\defauthor{nat}
\def\defauthor{}

%% option: largefont
\documentclass[square]{article} %
%% options: vscreen, garamond, wnotes, savespace
\usepackage[vscreen]{nat}
\usepackage[longnamesfirst]{natbib}
\bibpunct{(}{)}{;}{a}{,}{,}
\usepackage{amsfonts,amssymb,amsthm} %
\usepackage[tbtags]{amsmath} %
\usepackage{bm}

% \usepackage{fullpage}

\usepackage{graphicx,color}
\graphicspath{{./pics/}}
\definecolor{BrickRed}{rgb}{.625,.25,.25}
\providecommand{\red}[1]{\textcolor{BrickRed}{#1}}
\definecolor{markergreen}{rgb}{0.6, 1.0, 0}
\definecolor{darkgreen}{rgb}{0, .5, 0}
\definecolor{darkred}{rgb}{.7,0,0}
\providecommand{\marker}[1]{\fcolorbox{markergreen}{markergreen}{{#1}}}
\providecommand{\natp}[1]{\textcolor{darkred}{#1}}
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}%[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary} %%
\newtheorem{lemma}[theorem]{Lemma} %%
\theoremstyle{definition} %%
\newtheorem{definition}{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{remarks}{Remarks}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{example}[theorem]{Example}
\newtheorem{assumption}{Assumption}

\usepackage[makestderr]{pythontex}
\usepackage{amsmath}
\begin{pycode}
import numpy as np
from scipy import stats
import statsmodels.api as sm
import pandas as pd
import matplotlib.pyplot as plt
np.random.seed(87654)
\end{pycode}


\input{definitions}
\sloppy
\begin{document}
\setlength{\boxlength}{0.95\textwidth} %
\title{\large{\bf\deftitle}} %
\author{{\normalsize\bf\defauthor}}%
\thispagestyle{empty}
\addtocounter{page}{1}
\maketitle
\begin{abstract}
  We investigate different methods of hedging cryptocurrencies with
  Bitcoin futures. A useful generalisation of variance-based hedging
  uses spectral risk measures and copulas. 
\end{abstract}
% \keywords{keywords here} %%
% \jel{jel here} %%
\vspace{.5cm}
\def\contentsname{Contents}
\tableofcontents
%%
\vspace{.5cm}
%\clearpage

\section{Optimal hedge ratio}
\label{sec:optimal-hedge-ratio}

Following \citep{Barbi2014}, we consider the problem of the optimal
hedge ratios by extending commmonly known minimum variance hedge ratio
to more general risk measures and dependence structures.\medskip\\
Hedge portfolio: $R_t^h = R_t^S - h R_t^F$, involving returns of spot
and future contract and where $h$ is the hedge ratio\\
Optimal hedge ratio: $h^\ast = \argmin_h \rho_\phi(s,h)$, for given
confidence level $1-s$ (if applicable, e.g.\ in the case of VaR, ES),
where $\rho_\phi$ is a spectral risk measure with weighting function
$\phi$ (see below). \\ 
Corollary 2.1 of \citep{Barbi2014}, corrected:
\begin{proposition}
  Let $R^S$ and $R^F$ be two real-valued random variables on the same
  probability space $(\Omega, \mathcal A, \p)$ with corresponding
  absolutely continuous copula $C^t_{R^S, R^F}(w,\lambda)$ and
  continuous marginals $F_{R^S}$ and $F_{R^F}$. Then, the distribution
  of of $R^h$ is given by
  \begin{equation*}
    F_{R^h}(x) = 1- \int^1_0 D_1 C_{R^S, R^F}
    \left( u, F_{R^F} \left[ \frac{F^{-1}_{R^S}(u)-x}{h} \right]
    \right)\, \dd u.  
  \end{equation*}
\end{proposition}
The proof uses the $D_1$-operator 
Here $D_1 C(u,v)=\displaystyle \frac{\partial}{\partial u} C(u,v)$,
which can be shown to fulfil \citep{Cherubini2011}
\begin{equation}
  \label{eq:1}
  D_1 C_{X,Y}(F_X(x), F_Y(y)) = \p(Y\leq y|X=x).
\end{equation}
\begin{proof}
  Using the identity (\ref{eq:1}) gives
  \begin{align*}
    F_{R^h}(x) &= \p(R^s - h R^F\leq x) %
                 = \E\left[\p\left(R^F\geq \frac{R^S-x}{h}\Big|
                 R^S\right)\right]\\[10pt]
               &= 1-\E\left[\p\left(R^F\leq \frac{R^S-x}{h}\Big|
                 R^S\right)\right]\\[10pt] 
               &= 1- \int_0^1 D_1 C_{R^S, R^F}\left(u,
                 F_{R^F}\left(\frac{F^{(-1)}_{R^S}(u) -
                 x}{h}\right)\right)\, \dd u.
  \end{align*}
\end{proof}

\subsection{Special case: Gaussian copula}
\label{sec:spec-case:-gauss}

Let $R^S\sim \Ncdf(\mu_S, \sigma_S^2)$ and $R^F\sim \Ncdf(\mu_F,
\sigma_F^2)$ and assume further that they are jointly normally
distributed with correlation $\rho$. Then,
\begin{equation*}
  R^h = R^S - h R^F \sim \Ncdf(\mu_S - h \mu_F, \sigma_s^2 + h^2
  \sigma_F^2 - 2\rho h \sigma_S \sigma_F).
\end{equation*}
More generally, if $R^k\sim F^k$, $k\in \{S,F\}$, then
\begin{align*}
  \p(R^S-h R^F\leq x)
  &= 1-\E\left[ \p\left(R^F\leq \frac{R^S-x}{h}\big| R^S\right)\right] \\ %
  &= 1-\E\left[\p \left(\Ncdf^{(-1)}(F_F(R^F)) \leq
    \Ncdf^{(-1)}\left(F_F\left(\frac{R^S-x}{h}\right)\right) \Big|
    R^S\right)\right] \\%
  &= 1-\E\left[ \p\left(\rho \Ncdf^{(-1)}(F_S(R^S)) + \sqrt{1-\rho^2}
    \varepsilon \leq \Ncdf^{(-1)}\left(F_F\left(\frac{R^S-x}{h}\right)\right) \Big|
    R^S\right)\right]\\ %
  &= 1-\E\left[ \Ncdf \left(
    \frac{\Ncdf^{(-1)}\left(F_F\left(\frac{R^S-x}{h}\right)\right) -\rho
    \Ncdf^{(-1)}(F_S(R^S))} { \sqrt{1-\rho^2}}\right)\right]\\
  &= 1-\int_0^1  \Ncdf \left(
    \frac{\Ncdf^{(-1)}\left(F_F\left(\frac{F_S^{(-1)}(u)-x}{h}\right)\right) -\rho
    \Ncdf^{(-1)}(u)} { \sqrt{1-\rho^2}}\right) \,\dd u.
\end{align*}


\section{Special case: Normal variance mixtures}
\label{sec:special-case:-normal}

Let $(R^S, R^F)$ follow a normal variance mixture, i.e., there exists a
decomposition such that
\begin{align*}
  R^S &=\mu_S + \sqrt{W} \sigma_S Z_1\\
  R^F &= \mu_F + \sqrt{W} \sigma_F (\rho Z_1 + \sqrt{1-\rho^2} Z_2),
\end{align*}
where $W$ is the mixing variable and $Z_1, Z_2$ are independent
standard normal variables. Then, $R^h$ follows a NVM distribution with
\begin{equation*}
  R^h = R^S - h R^F =  \mu_S - h \mu_F + \sqrt{W}
  \left((\sigma_S-h\sigma_F\rho)Z_1 -h \sqrt{1-\rho^2} 
    \sigma_F Z_2\right) = \mu_S - h \mu_F + \sqrt{W} Z_3,
\end{equation*}
where $Z_3\sim \Ncdf(0, \sigma_S^2 + h^2\sigma_F^2 - 2\rho
h\sigma_S \sigma_F)$. 

More generally, let $R^k\sim F^k$, $k\in \{S,F\}$ and write $V$
as the marginal distribution functions of the NVM distribution
components. Let $V^{(-1)}(F_S(R^S)) = \sqrt{W} Z_1$ and $V^{(-1)}(F_F(R^F)) =
\sqrt{W} \rho Z_1 + \sqrt{W} \sqrt{1-\rho^2} Z_2$, were $Z_1, Z_2$ are
independent standard normals. Then 
\begin{align*}
  \p(R^S-h R^F\leq x)
  &= 1-\E\left[ \p\left(R^F\leq \frac{R^S-x}{h}\big| R^S\right)\right] \\ %
  &= 1-\E\left[\p \left(V^{(-1)}(F_F(R^F)) \leq
    V^{(-1)}\left(F_F\left(\frac{R^S-x}{h}\right)\right) \Big|
    W, Z_1\right)\right] \\%
  &= 1-\E\left[ \p\left(\sqrt{W} \rho Z_1 + \sqrt{W} \sqrt{1-\rho^2}
    Z_2\leq V^{(-1)}\left(F_F\left(\frac{F_S^{(-1)}(V(\sqrt{W}
    Z_1))-x}{h}\right)\right) \Big| W, Z_1\right)\right]\\ %
  &= 1-\E\left[ \Ncdf \left(
    \frac{V^{(-1)}\left(F_F\left(\frac{F_S^{(-1)}(V(\sqrt{W}
    Z_1))-x}{h}\right)\right) -\rho \sqrt{W} Z_1} {
    \sqrt{W}\sqrt{1-\rho^2}}\right)\right]\\ 
  &= 1-\int_0^\infty \int_{-\infty}^{\infty} \Ncdf \left(
    \frac{V^{(-1)}\left(F_F\left(\frac{F_S^{(-1)}(V(\sqrt{w}
    z_1))-x}{h}\right)\right) -\rho\sqrt{w} z_1} { \sqrt{w}
    \sqrt{1-\rho^2}}\right) \, \varphi(z_1)\, f_W(w)\, \dd z_1\, \dd
    w\\
  &= 1-\int_0^1 \int_{-\infty}^\infty  \Ncdf \left(
    \frac{V^{(-1)}\left(F_F\left(\frac{F_S^{(-1)}(u)-x}{h}\right)\right)
    -\rho V^{(-1)}(u)} { V^{(-1)}(u)/z_1
    \sqrt{1-\rho^2}}\right) \, \varphi(z_1)\, \dd z_1\, \dd
    u\\
\end{align*}





\section{Spectral risk measures}
\label{sec:spectr-risk-meas}

Spectral risk measure \citep{Acerbi2002,Cotter2006}:
\begin{equation*}
\rho_\phi = -\int_0^1 \phi(p)\, q_p\, \dd p,
\end{equation*}
where $q_p$ is the $p$-quantile of the return distribution and
$\phi(s)$, $s\in [0,1]$, is the so-called {\em risk aversion
  function\/}, a weighting function such that\footnote{Note that the
  treatment in \citep{Acerbi2002} is measure-based and therefore
  slightly different} 
\begin{enumerate}[(i)]
\item $\phi(p)\geq 0$,
\item $\int_0^1\phi(p)\, \dd p=1$,
\item $\phi'(p)\leq 0$. 
\end{enumerate}
Examples: VaR, ES\\
Replacing the last property with $\phi'(p)>0$ rules out risk-neutral
behaviour. \\
Spectral risk measures are coherent \citep{Acerbi2002}. 

\subsection{Representation of spectral risk measures}
\label{sec:repr-spectr-risk}

To prevent numerical instabilities involving the quantile function,
re-write spectral risk measures as follows:
\begin{itemize}
\item Integration by substitution: $\displaystyle \int_a^b
  g(\varphi(x)) \,\varphi'(x)\, \dd x = \int_{\varphi(a)}^{\varphi(b)}
  g(u)\, \dd u$.
\item Spectral risk measures: $\displaystyle -\int_0^1 \phi(p) \,
  F^{(-1)}(p)\, \dd p$
\item Set $\varphi(x)=F(x)$, $g(p) = \phi(p)\, F^{(-1)}(p)$.
\item Then:
  \begin{equation*}
    -\int_0^1 \phi(p)\, F^{(-1)}(p)\, \dd p = -\int_{-\infty}^\infty
    \phi(F(x))\, x\, f(x)\, \dd x.
  \end{equation*}
\end{itemize}


\subsection{Exponential spectral risk measures}
\label{sec:expon-risk-meas}

\begin{itemize}
\item Choose exponential utiliy function:
  $\displaystyle U(x) = -\e^{-k x}$, where $k>0$ is the Arrow-Pratt
  coefficient of absolute risk aversion
  (ARA).
\item Coefficient of absolute risk aversion: $\displaystyle R_A(x) =
  -\frac{U''(x)}{U'(x)} = k$
\item Coefficient of relative risk aversion: $\displaystyle R_R(x) = -
  \frac{x U''(x)}{U'(x)} = xk$
\item Weighting function $\phi(p) = \lambda \e^{-k(1-p)}$, where
  $\lambda$ is an unknown positive constant.
\item Set $\displaystyle\lambda = \frac{k}{1-\e^{-k}}$ to satisfy
  normalisation.
\item Exponential spectral risk measure:
  \begin{equation*}
    \rho_{\phi} = \int_0^1 \phi(p)\, F^{(-1)}(p)\, \dd p =
    \frac{k}{1-\e^{-k}} \int_0^1 \e^{-k(1-p)}\, F^{(-1)}(p)\, \dd p. 
  \end{equation*}
(If calculation of quantiles is a problem use change of variables
above.)
\item What exactly is the link between risk measure and utility?
    I think there is no direct link: the exponential risk measure is
   {\em inspired\/} by ARA utility.
\end{itemize}


\input{D1Operator.tex}

\section{Dependence}
\label{sec:dependence}
\input{dependence.tex}

\newpage
\section{Estimation}
\input{estimation.tex}


\newpage
\bibliographystyle{abbrvnamed} %
\bibliography{finance} %
\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
